Allocate landings to Georges Bank EPU

### 2020-12-04 docs/allocateLandingsEPU.Rmd
remove chapter numbering

---
title: "Allocate landings to Georges Bank EPU"
author: Andy Beet
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  bookdown::html_document2:
    code_fold: hide
csl: apa-annotated-bibliography.csl
bibliography: references.bib
---

>>>>

---
title: "Allocate landings to Georges Bank EPU"
author: Andy Beet
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  bookdown::html_document2:
    code_fold: hide
    number_sections: false
csl: apa-annotated-bibliography.csl
bibliography: references.bib
---
